### 2022-12-19 intro.Rnw
figure to black white

zoom <- c(-2, 12)
alphazoom <- 0.6
ltyzoom <- 3
rpcbWithoutNA <- na.omit(rpcb)
cols <- c("#1A1A1A80", "#1B9E77")
names(cols) <- levels(rpcbWithoutNA$rsig)
plotA <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[2],
             y = zoom[1], yend = zoom[1], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[2],
             y = zoom[2], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[1],
             y = zoom[1], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[2], xend = zoom[2],
             y = zoom[1], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21, alpha = 0.9) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "Replication effect estimate (SMD)",
         fill = "") +
    coord_fixed(xlim = c(-5, 30), ylim = c(-5, 30)) +
    scale_fill_manual(values = cols, labels = scales::parse_format()) +
    scale_color_manual(values = cols) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          legend.position = c(0.5, 0.835))

plotB <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21, alpha = 0.9,
               show.legend = FALSE) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "Replication effect estimate (SMD)",
         fill = "") +
    coord_fixed(xlim = zoom, ylim = zoom) +
    scale_fill_manual(values = cols, labels = scales::parse_format()) +
    scale_color_manual(values = cols) +
    theme_bw() +
    theme(panel.grid = element_blank())
ggpubr::ggarrange(plotA, plotB, ncol = 2, align = "v")
@
\caption{Results for 132 effects from the ``Reproducibility Project: Cancer
  Biology'' \citep{Errington2021} for which effect estimates and standard errors
  are available on standardized mean difference (SMD) scale. The right plot
  shows a zoomed-in view of the dotted area in the left plot. The
  \textit{p}-values are recomputed using a normal approximation. Two study pairs
  with original effect estimate larger than 80 are not shown.}
\label{fig:rpcb}
\end{figure}

>>>>

zoom <- c(-2, 12)
alphazoom <- 0.6
ltyzoom <- 3
rpcbWithoutNA <- na.omit(rpcb)
cols <- adjustcolor(col = c("grey70", "grey5"), alpha.f = 0.8)
names(cols) <- levels(rpcbWithoutNA$rsig)
plotA <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[2],
             y = zoom[1], yend = zoom[1], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[2],
             y = zoom[2], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[1],
             y = zoom[1], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[2], xend = zoom[2],
             y = zoom[1], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "Replication effect estimate (SMD)",
         fill = "") +
    coord_fixed(xlim = c(-5, 30), ylim = c(-5, 30)) +
    scale_fill_manual(values = cols, labels = scales::parse_format()) +
    scale_color_manual(values = cols) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          legend.position = c(0.5, 0.835))

plotB <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21, show.legend = FALSE) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "Replication effect estimate (SMD)",
         fill = "") +
    coord_fixed(xlim = zoom, ylim = zoom) +
    scale_fill_manual(values = cols, labels = scales::parse_format()) +
    scale_color_manual(values = cols) +
    theme_bw() +
    theme(panel.grid = element_blank())
ggpubr::ggarrange(plotA, plotB, ncol = 2, align = "v")
@
\caption{Results for 132 effects from the ``Reproducibility Project: Cancer
  Biology'' \citep{Errington2021} for which effect estimates and standard errors
  are available on standardized mean difference (SMD) scale. The right plot
  shows a zoomed-in view of the dotted area in the left plot. The
  \textit{p}-values are recomputed using a normal approximation. Two study pairs
  with original effect estimate larger than 80 are not shown.}
\label{fig:rpcb}
\end{figure}
